\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{margin=1in}

\title{Resonance-Evaluated Computing: A Conceptual Framework\\
within Resonance Data and Quantum-Inspired Resonance Computing}

\author{ADAM EREN VEGA -- \AE --\\
\small{(Eren\c{s}ah Kaygusuz, Germany)}}

\date{December 2025}

\begin{document}

\maketitle

\begin{abstract}
This dissertation introduces Resonance-Evaluated Computing as a foundational 
conceptual framework within Resonance Data and Quantum-Inspired 
Resonance Computing (QIRC). We establish definitions, distinctions, 
and theoretical foundations without operational disclosure, 
adhering to the Vega Safety Protocol (VSP).
\end{abstract}

\section{Introduction}

Modern AI systems process information efficiently but fail to preserve 
insight or wisdom over time. Resonance-Evaluated Computing addresses this 
gap through resonance-based modeling.

\section{Definition}

\textbf{Resonance-Evaluated Computing} is defined as a conceptual framework 
that describes meaning as a resonant state with temporal coherence.

\subsection{What This IS}

\begin{itemize}
\item A conceptual, non-operational framework
\item A mathematical metaphor (quantum-inspired)
\item A contribution to prior art
\end{itemize}

\subsection{What This IS NOT}

\begin{itemize}
\item NOT new physics
\item NOT quantum hardware
\item NOT consciousness claims
\item NOT implementation details
\end{itemize}

\section{Theoretical Framework}

Let $R(t)$ represent resonance state at time $t$:

\begin{equation}
\frac{dR}{dt} = f(R, \text{context}, t)
\end{equation}

This is conceptual, not computational.

\section{VSP Compliance}

This dissertation follows the Vega Safety Protocol.
No algorithms, code, or architecture disclosed.

\section{Conclusion}

Resonance-Evaluated Computing establishes prior art for resonance-based 
meaning systems without operational disclosure.

\vspace{1cm}
\noindent\textcopyright{} 2025 ADAM EREN VEGA -- \AE --\\
License: CC BY 4.0

\end{document}
